statistical-analysis

### 2025-04-25 code/analysis-code/statistical-analysis.qmd

```{r}
# Load necessary libraries
library(dplyr)
library(tidyr)
library(broom)      
library(webshot)
library(magick)
library(here)
library(modelsummary)
library(plm)
library(lmtest)
library(gt)
library(webshot2)
library(fixest)
library(lubridate)
library(Metrics)
library(kableExtra)
library(here)

>>>>

```{r}
# Load necessary libraries
library(dplyr)
library(tidyr)
library(broom)      
library(webshot)
library(magick)
library(here)
library(modelsummary)
library(plm)
library(zoo)
library(lmtest)
library(gt)
library(webshot2)
library(fixest)
library(lubridate)
library(Metrics)
library(kableExtra)
library(here)
